Finch: A Datastructure-Driven Array Programming Language

### 2024-03-14 main.tex
Update on Overleaf.
cool

@@

\subsubsection{RLE Blur}

-Compare against the zip/unzip version

- Which Datasets? Check taco-rle or looplets.
(perhaps consider if a neural network is the right call here)

\subsubsection{Histogram}

\subsubsection{Graph Applications}
\begin{figure}
	\includegraphics[width=\linewidth]{bfs_speedup_over_graphs.jl.png}
	\includegraphics[width=\linewidth]{bellmanford_speedup_over_graphs.jl.png}
    \caption{Performance of graph apps across various tools.}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{spmv_performance_grouped.png}
    \caption{Performance of SpMV by Finch format.}
\end{figure}

@@

\subsubsection{Image Morphology}

\begin{figure}
	\includegraphics[width=\linewidth]{erode4_speedup_over_opencv.png}
    \caption{Performance of Finch on erosion task (4 iterations).}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{hist_speedup_over_opencv.png}
    \caption{Performance of Finch on masked histogram task.}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{fill_speedup_over_opencv.png}
    \caption{Performance of Finch on flood fill task.}
\end{figure}

\subsubsection{Graph Analytics}
\begin{figure}
	\includegraphics[width=\linewidth]{bfs_speedup_over_graphs.jl.png}
	\includegraphics[width=\linewidth]{bellmanford_speedup_over_graphs.jl.png}
    \caption{Performance of graph apps across various tools.}
\end{figure}
